### 2024-02-20 paper_sisc_first_revision/localpsf.tex
define polylig linear

The computational cost of the PSF-based method may be divided into the costs to perform the following tasks: (1) Computing impulse response moments and batches (Lines 1 and 4 in Algorithm \ref{alg:construct_Atilde}); (2) Building the H-matrix (Lines 5 and 6 in Algorithm \ref{alg:construct_Atilde}); (3) Performing linear algebra operations with the H-matrix. This may optionally include the symmetric positive semi-definite modifications described in Section \ref{sec:flip_eigs}. In target applications, (1) is the dominant cost because applying $\Aop$ to a vector requires an expensive computational procedure such as solving a PDE, and (1) is the only step that requires applying $\Aop$ to vectors.
All operations that do not require applications of $\Aop$ to vectors are polylog linear, and therefore scalable, in the size of the problem, $N$.
We now describe these costs in detail. For convenience, Table~\ref{tab:vars} lists variable symbols and their approximate sizes.

>>>>

The computational cost of the PSF-based method may be divided into the costs to perform the following tasks: (1) Computing impulse response moments and batches (Lines 1 and 4 in Algorithm \ref{alg:construct_Atilde}); (2) Building the H-matrix (Lines 5 and 6 in Algorithm \ref{alg:construct_Atilde}); (3) Performing linear algebra operations with the H-matrix. This may optionally include the symmetric positive semi-definite modifications described in Section \ref{sec:flip_eigs}. In target applications, (1) is the dominant cost because applying $\Aop$ to a vector requires an expensive computational procedure such as solving a PDE, and (1) is the only step that requires applying $\Aop$ to vectors.
All operations that do not require applications of $\Aop$ to vectors are polylog linear (i.e., $O(N \log(N)^b)$ for some $b$), and therefore scalable, in the size of the problem, $N$.
We now describe these costs in detail. For convenience, Table~\ref{tab:vars} lists variable symbols and their approximate sizes.
